---
title: On the Surgical Removal of Cardassian Cranial Implants
subtitle: A case study of a Cardassian patient
date: "`r Sys.Date()`"
author:
  - name: Julian Bashir
    affiliations: 
      - id: ds9
        address: | 
          Starbase Deep Space Nine
          Sick Bay
          1234 Main Street
          Anytown, NY 90210
  - name: Elim Garak
    affiliations:
      - id: terok
        address: | 
          Terok Nor
          Promenade
      - ref: ds9
target-journal:
  - Starfleet Academy
abstract: |
  Space: the final frontier. These are the voyages of the starship *Enterprise*. Its continuing mission: to explore strange new worlds. To seek out new life and new civilizations. To boldly go where no one has gone before! Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.
keywords:
  - surgery
  - espionage
  - brains
corresponding_author: jbashir2341@starfleet.edu
bibliography: example.bib
linenumbers: true
watermark: true
format:
  simple-pdf: default
---

We're acquainted with the wormhole phenomenon, but this... Is a remarkable piece of bio-electronic engineering by which I see much of the EM spectrum ranging from heat and infrared through radio waves, et cetera, and forgive me if I've said and listened to this a thousand times [@Lovelace:1842]. This planet's interior heat provides an abundance of geothermal energy. We need to neutralize the homing signal. [http://ctan.org/pkg/hyperref](http://ctan.org/pkg/hyperref) Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.


# Main section

It indicates a synchronic distortion in the areas emanating triolic waves. The cerebellum, the cerebral cortex, the brain stem,  the entire nervous system has been depleted of electrochemical energy [@Turing:1936]. Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.

```{r}
n_lights <- 2 + 2
n_lights
```

Any device like that would produce high levels of triolic waves. These walls have undergone some kind of selective molecular polarization. I haven't determined if our phaser energy can generate a stable field. We could alter the photons with phase discriminators. Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.

$$
y = \text{Something} + \beta_1 x_1
$$

Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems. Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.

## Subsection

Communication is not possible [@Keynes:1937]. The shuttle has no power (see @fig-n-lights). Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.

Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems. 

Assemble a team. Look at records of the Drema quadrant. Would these scans detect artificial transmissions as well as natural signals?

```{r plot-n-lights}
#| echo: false
#| label: fig-n-lights
#| fig-cap: There are four lights
#| fig-width: 5
#| fig-height: 1
#| fig-align: "center"
par(mar = c(0, 0, 0, 0))
plot(x = seq(1:n_lights), y = rep(1, 4), col = "darkgoldenrod1", 
     pch = 8, cex = 4, axes = TRUE, ann = FALSE, xlab = FALSE, ylab = FALSE)
```

Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.

## Other heading

Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illoUsing the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.

### Third

inventore veritatis^[Thing] et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est,^[Another thing] 

qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. 

#### A 4th level heading

qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems.